Bootstrap Confidence Intervals for Sharp Regression Discontinuity Designs

### 2016-08-30 main_paper.tex
[WIP] Fix error at end of Theorem 2 proof
Closes #25.
Fix a typo in Assumption 2
We accidentally deleted the limit. This commit add the limit "0".

\begin{assumption}[Bandwidth and kernel]\label{A2}
  Let $h$ be the bandwidth used to estimate the local linear model and let
  $b$ be the bandwidth used to estimate a second local quadratic model. Then
  $n h \to \infty$, $n b \to \infty$, and
  $n \times \min(h, b)^{5} \times \max(h, b)^2$ as $n \to \infty$.\footnote{%
    Unless otherwise stated, all limits in this paper are assumed to hold as
    $n \to \infty$.}
  The kernel function $K$ is positive, bounded, and continuous on the interval
  $[-\kappa,~\kappa]$ and zero outside that interval for some $\kappa > 0$.
\end{assumption}
To simplify notation, let $m = \min(h,b)$ and
define the scaled and truncated kernel functions
\begin{align*}
  K_{+,h}(x) &= \tfrac{1}{h} K(x/h) \1\{x \geq 0\} &
  K_{-,h}(x) &= \tfrac{1}{h} K(x/h) \1\{x < 0\}
\intertext{and}
  K_{+,b}(x) &= \tfrac{1}{b} K(x/b) \1\{x \geq 0\} &
  K_{-,b}(x) &= \tfrac{1}{b} K(x/b) \1\{x < 0\}.
\end{align*}
Assumption~\ref{A2} allows for the vast majority kernel functions commonly used
in practice. Note that different kernel functions could be used for the
treatment effect estimator and the higher order approximation used for the
bootstrap.\footnote{%
  It would be a slight abuse of notation for $K_{+,h}$, $K_{-,h}$,
  $K_{+,b}$, and $K_{-,b}$ to all use different underlying kernels but
  would not affect our proofs.} %
For simplicity, however, we use the same function for all steps of
estimation in this paper.  Potentially different kernel functions and bandwidths
could also be used for estimation below and above the cutoff, but we again focus
on the simpler case here.

@@

Normality also follows standard arguments for the wild
bootstrap. Conditional on the regressors and residuals,
$\{R(X_i) \hat\varepsilon_i e_i^* \}$ is a sequence of independent and
mean zero random variables for any measurable function $R$, each with
$q$th absolute moment
$\lvert R(X_i) \hat\varepsilon_i \rvert^q \E \lvert e_i^*
\rvert^{q}$.
The result then holds as a consequence of the Lindeberg-Feller CLT if
we establish that Liapunov's condition holds in probability, specifically that
\begin{equation}\label{eq:17}
  (\tfrac{m}{n})^{1+\delta/2} \sum_{i} \lvert (R_+(X_i) - R_-(X_i))
  \hat\varepsilon_i \rvert^{2+\delta} \to^{p} 0.
\end{equation}
with
\begin{equation*}
  R_\bullet(X_i) = \gamma_1' r_1(X_i/h) K_{\bullet,h}(X_i) +
  (h/b)^2 \cdot \gamma_2' r_2(X_i/b) K_{\bullet,b}(X_i)
\end{equation*}
for arbitrary nonzero vectors $\gamma_1$ and $\gamma_2$.
\citep[See, for example,][Proposition 2.27 and Theorem 23.4.]{VDV00}
But similar arguments to those used for the variance establish
that
\begin{equation}\label{eq:17}
  \tfrac{1}{n} \sum_{i} m^{1+\delta} \lvert (R_+(X_i) - R_-(X_i))
  \hat\varepsilon_i \rvert^{2+\delta}.
\end{equation}
obeys the LLN, implying that~\eqref{eq:17} holds and completing the proof. \qed

>>>>

\begin{assumption}[Bandwidth and kernel]\label{A2}
  Let $h$ be the bandwidth used to estimate the local linear model and let
  $b$ be the bandwidth used to estimate a second local quadratic model. Then
  $n h \to \infty$, $n b \to \infty$, and
  $n \times \min(h, b)^{5} \times \max(h, b)^2 \to 0$ as $n \to \infty$.\footnote{%
    Unless otherwise stated, all limits in this paper are assumed to hold as
    $n \to \infty$.}
  The kernel function $K$ is positive, bounded, and continuous on the interval
  $[-\kappa,~\kappa]$ and zero outside that interval for some $\kappa > 0$.
\end{assumption}
To simplify notation, let $m = \min(h,b)$ and
define the scaled and truncated kernel functions
\begin{align*}
  K_{+,h}(x) &= \tfrac{1}{h} K(x/h) \1\{x \geq 0\} &
  K_{-,h}(x) &= \tfrac{1}{h} K(x/h) \1\{x < 0\}
\intertext{and}
  K_{+,b}(x) &= \tfrac{1}{b} K(x/b) \1\{x \geq 0\} &
  K_{-,b}(x) &= \tfrac{1}{b} K(x/b) \1\{x < 0\}.
\end{align*}
Assumption~\ref{A2} allows for the vast majority kernel functions commonly used
in practice. Note that different kernel functions could be used for the
treatment effect estimator and the higher order approximation used for the
bootstrap.\footnote{%
  It would be a slight abuse of notation for $K_{+,h}$, $K_{-,h}$,
  $K_{+,b}$, and $K_{-,b}$ to all use different underlying kernels but
  would not affect our proofs.} %
For simplicity, however, we use the same function for all steps of
estimation in this paper.  Potentially different kernel functions and bandwidths
could also be used for estimation below and above the cutoff, but we again focus
on the simpler case here.

@@

Normality also follows standard arguments for the wild
bootstrap. Conditional on the regressors and residuals,
$\{R(X_i) \hat\varepsilon_i e_i^* \}$ is a sequence of independent and
mean zero random variables for any measurable function $R$, each with
$q$th absolute moment
$\lvert R(X_i) \hat\varepsilon_i \rvert^q \E \lvert e_i^*
\rvert^{q}$.
The result then holds as a consequence of the Lindeberg-Feller CLT if
we establish that Liapunov's condition holds in probability, specifically that
\begin{equation}\label{eq:17}
  \big(\tfrac{1}{n}\big)^{1+\delta/2} \sum_{i} \lvert (R_+(X_i) - R_-(X_i))
  \hat\varepsilon_i \rvert^{2+\delta} \to^{p} 0.
\end{equation}
with
\begin{equation*}
  R_\bullet(X_i) = h^{1/2} \cdot \gamma_1' r_1(X_i/h) K_{\bullet,h}(X_i)
  + b^{1/2} \cdot \gamma_2' r_2(X_i/b) K_{\bullet,b}(X_i)
\end{equation*}
for arbitrary nonzero vectors $\gamma_1$ and $\gamma_2$.
\citep[See, for example,][Proposition 2.27 and Theorem 23.4.]{VDV00}
But similar arguments to those used for the variance establish
that
\begin{equation}\label{eq:16}
  \tfrac{1}{n} \sum_{i} \lvert (R_+(X_i) - R_-(X_i))
  \hat\varepsilon_i \rvert^{2+\delta}
  = O_p(h^{-\delta/2}) + O_p(b^{-\delta/2}).
\end{equation}
Since $nb \to \infty$ and $n h \to \infty$ by
assumption,~\eqref{eq:16} implies that~\eqref{eq:17} holds and
completes the proof. \qed
